\cvitemwithcomment{Programming language}{C, C++, Java, JavaScript, Html5, CSS, PHP, SQL, Bash}{}

\cvitemwithcomment{}{Python}{Implementation of scripts for scheduled tasks. Implementation of desktop applications to obtain and evaluate multiple linear regression models using different statistical processing and data science packages such as \emph{Matplotlib}, \emph{Pandas}, \emph{Numpy}, \emph{Scipy } and \emph{Statsmodels}. Implementation of desktop applications for the management, control and status check of certain processes in Unix operating systems. Implementation of modules for the connection and consumption of API data from the applications. Implementation of solutions to competitive programming problems. }
\cvitemwithcomment{Operating systems}{Debian, Ubuntu, Window, Android}{}
\cvitemwithcomment{Frameworks}{Qt, Yii, CodeIngiter, JQuery, AngularJS, W3CSS, Bootstrap}{}
\cvitemwithcomment{}{Django}{Implementation of web systems for the management of human resources, tourist resources, control and planning of activities, generation of payroll for human resources in Excel and PDF format. Implementation of APIs using \emph{django-rest-framework} for the communication of other applications with a system developed in Django. Customizing the Django admin panel. Implementation of multilingual systems not only in the graphical user interface but also in the content stored in the database.}

\cvitemwithcomment{Content management system}{Joomla, WordPress}{}
\cvitemwithcomment{}{Moodle}{Installation and deployment on servers with Ubuntu and Debian with Mariadb database manager. Personalization, configuration and adinstration of the platform. Administration, management and assembly of courses on the platform. Development of extensions of the report, themes and block types. Development of applications that consume the API that provides the platform. Examples of deployments performed: \href {https://eva.umcc.cu/pregrado} {Eva Undergraduate}, \href {https://eva.umcc.cu/posgrado} {Eva Postgraduate}, \href{https://eva.umcc.cu/mooc}{Eva MOOC} (you can click on the names to view)}

\cvitemwithcomment{ERP}{Odoo}{Development of basic addon structures in Odoo versions 12, 15, 16, and
 17. Implementation of addons that consume external APIs and convert data into Odoo models. Management and creation of scheduled tasks within the Odoo environment. Design of visual interfaces
for forms and tree views.}

\cvitemwithcomment{Database manager}{Postgres, MySql, MariaDB}{}

\cvitemwithcomment{2D graphic design}{Gimp, Inkscape}{}

\cvitemwithcomment{CASE Tool}{Visual Paradigm}{}

\cvitemwithcomment{Web server}{Apache, XAMPP, NGINX}{}

\cvitemwithcomment{Text processor}{LaTex}{}

\cvitemwithcomment{Version control}{Git}{}

\cvitemwithcomment{Software development methodology}{Extreme Programming (XP)}{}