\cvitem{title}{ROFLEXIN/LC System Man-Machine Interface Viewer for Mobile Devices.}
\cvitem{tutors}{Ph.D Ramón Quiza Sardiñas}
\cvitem{description}{  The Center for Studies on Advanced and Sustainable Manufacturing (CEFAS) of the University of Matanzas develops the ROFLEXIN/LC project: Robust, flexible and intelligent, low-cost system for monitoring systems and mechanical processes. This project is fundamentally aimed at small and medium-sized companies, where the use of the alternatives available in the world market is not financially feasible. The present investigation arises from the need of the personnel that uses the ROFLEXIN/LC, to visualize the information collected by said system in mobile devices and tablets. The fundamental objective is to develop a mobile application capable of visualizing the information of the ROFLEXIN/LC system in real time. For the development of the proposed solution, an analysis of the main tools, technologies and methodologies used in the construction of software is carried out. The process was guided by the use of the following tools and technologies: {\em Visual Paradigm} as a CASE tool, UML as a modeling language, JSON as a data exchange format, and Java as a programming language. Developed with the Eclipse IDE with the ADT extension. To validate that the results achieved were those expected, a set of tests was carried out. It was possible to correct all the detected non-conformities, which means that the proposed solution is ready to be deployed. Finally, a Viewer for mobile devices and tablets with Android operating system capable of representing in real time the information coming from the ROFLEXIN/LC system was obtained. }

%\subsection{Vocational}
